---
title: "Power analysis: Expertise, complexity, age"
author: "Meltem Ozcan"
date: "1/9/2021"
output: html_document
toc: true
---

```{r, include=FALSE}
library(glmmTMB)
library(simr) #for makeGlmer
library(corpcor) #for make.pos.def
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
set.seed(77)
```

# Procedure

We are interested in exploring differences between age groups in their ability to
teach differentially to audiences of different levels of expertise (i.e. choosing 
to teach a basic fact to a baby and a complex fact to an adult). The comparison
between 4 year olds and 8 year olds is not meaningful - the groups we would like
to compare are 4 year olds vs. 6 year olds, and 6 year olds vs. 8 year olds. 
Thus, age will be coded as a binary variable for the models (rather than a 
categorical variable with three levels).

Each participant will receive each stimuli (12 pairs of statements about animals 
that are either basic or complex) in a sequence counterbalanced for complexity 
(basic first vs. complex first), 
expertise of audience (adult, baby), order of presentation of animals, as well 
as age and gender of participants. As each trial is nested within Animal (fact 
pairs; denoted $j$) and within Child (participants; denoted $k$), the design is 
cross classified at level 2.

The outcome $Y_{i(j,k)}$ is coded 1 for if a complex fact is taught to 
an adult or a basic fact is taught to a baby, and 0 otherwise. i refers to the observation(ex. $i=1,..., 768$ if 2 groups, 32 participants in each group). Each
trial outcome can be modeled using the Bernoulli distribution (1 for successful discriminative teaching based on expertise, 0 for failure). We will use a cross-classified multilevel logistic model. 

# Models
## Full model

**Repeated measure level (level 1):**
$$\text{Y}_{i(j,k)}=\beta_{0(j,k)}$$
**Between-cell (Child x Animal level/level 2)**, where the Animal variables can have
random slopes of Child, and Child variables can have random slopes for Animal (e.g.
maybe the infuence of age on the log odds of teaching correctly on a given item 
depends on whether the audience is a baby or an adult):
$$
\begin{align*}
\beta_{0(j,k)} &= \gamma_{00} \\ &\hspace{6mm} +
                    \beta_{1k}\text{condition}_{j} +
                    \beta_{2k}\text{information}_{j} \\
                     &\hspace{6mm} +
                    \beta_{3k}\text{condition}_{j}\times\text{information}_{j}\\
                    &\hspace{6mm} 
                    +\beta_{4j}\text{age}_k + 
                    \beta_{5j}\text{gender}_k\\
                    &\hspace{6mm}
                    +\beta_{6j}\text{age}_k \times \text{gender}_k\\
                    &\hspace{6mm} +u_{0j} + u_{0k}
\end{align*}
$$
$u_{0k}$ is the random intercept for Child, $u_{0j}$ is the random intercept 
for Animal, $\beta_{1k}$ and $\beta_{2k}$ are the main effects of condition and
information, $\beta_{4j}$ and $\beta_{5j}$ are the main effects of age and gender,
$\beta_{6j}$ is the effect of the interaction between age and gender, and 
$\beta_{3k}$ is the effect of the interaction between the manipulated condition 
and information variables.

**Child-level random slopes:**
$$
\begin{align*}
\beta_{1k}&=\gamma_{10}+\gamma_{11}\text{age}_{k}+\gamma_{12}\text{gender}_{k}+ u_{1k}\\
 \beta_{2k}&=\gamma_{20}+\gamma_{21}\text{age}_{k}+\gamma_{22}\text{gender}_{k}+ u_{2k}\\
\beta_{3k}&=\gamma_{30}+\gamma_{31}\text{age}_{k}+\gamma_{32}\text{gender}_{k}+ u_{3k}
\end{align*}
$$
The slopes of information and condition and the interaction of information and
condition might depend on/interact with the age and gender of the participant.
$u_{1k}, u_{2k}, u_{3k}$ are the random slopes.

**Animal-level random slopes:**
$$
\begin{align*}
                    \beta_{4j}&= \gamma_{40}+u_{4j}\\
                    \beta_{5j}&= \gamma_{50}+u_{5j}\\
                    \beta_{6j}&= \gamma_{60}+u_{6j}\\
\end{align*}
$$
**Full model:**

$$
\begin{align*}
\text{Y}_{i(j,k)}=&\gamma_{00} \\
                  +&\gamma_{10}\text{condition}_{j} \\
                  +&\gamma_{20}\text{information}_{j} \\
                  +&\gamma_{30}\text{condition}_{j}\times\text{information}_{j} \\
                  +&\gamma_{40}\text{age}_{k}\\
                  +&\gamma_{50}\text{gender}_k\\
                  +&\gamma_{60}\text{age}_k \times \text{gender}_k \\
                  +&\gamma_{11}\text{age}_{k}\times\text{condition}_{j} \\
                  +&\gamma_{12}\text{gender}_{k}\times\text{condition}_{j} \\
                  +&\gamma_{21}\text{age}_{k}\times\text{information}_{j} \\
                  +&\gamma_{22}\text{gender}_{k}\times\text{information}_{j} \\
                  +&\gamma_{31}\text{age}_{k}\times\text{condition}_{j}\times\text{information}_{j} \\
                  +&\gamma_{32}\text{gender}_{k}\times\text{condition}_{j}\times\text{information}_{j} \\
                  +&u_{0k} \\
                  +&u_{0j} \\
                  +&u_{1k}\text{condition}_{j} \\
                  +&u_{2k}\text{information}_{j} \\
                  +&u_{3k}\text{condition}_{j}\times\text{information}_{j} \\
                  +&u_{4j}\text{age}_k  \\
                  +&u_{5j}\text{gender}_k\\
                  +&u_{6j}\text{age}_k \times \text{gender}_k
\end{align*}
$$

$\gamma_{00}$ is the grand intercept; $\gamma_{10}$, $\gamma_{20}$, $\gamma_{30}$ 
are Animal-level main and interaction effects; $\gamma_{50}$, $\gamma_{50}$, $\gamma_{60}$ are Child-level main and interaction effects; $\gamma_{11}$, $\gamma_{12}$, $\gamma_{21}$, $\gamma_{22}$, $\gamma_{31}$, $\gamma_{32}$ 
are Animal x Child cross-level interactions; $u_{0k}$,$u_{1k}$,$u_{2k}$,$u_{3k}$ 
are Animal-level random intercept and slopes; and $u_{0j}$,$u_{4j}$,$u_{5j}$,
$u_{6j}$ are Child-level random intercept and slopes.

The full model takes into account effects and interactions that we may not be
interested in e.g. the three-way interaction between gender, condition, information.
To simplify the process, we will remove some terms that we don't have hypotheses 
for, such as the cross level interactions with gender and the interaction
between condition and information by setting $\gamma_{12}=0$,$\gamma_{22}=0$,
$\gamma_{30}$, $\gamma_{31}=0$ and $\gamma_{32}=0$ (as, for instance, there is no reason to think that the odds of any particular gender would be lower or higher 
for one of the two conditions). We will omit random slopes at this stage. 

## Reduced Model 1

We will keep the main effects and the main interactions of Animal and Child as
well as the random intercepts $u_{0k}$ and $u_{0j}$ (as the odds of success may 
be higher or lower in general for certain participants or stimuli). This leaves us with:

$$
\begin{align*}
\text{Y}_{i(j,k)}&=\gamma_{00} \\
                  &+\gamma_{10}\text{condition}_{j} \\
                  &+\gamma_{20}\text{information}_{j} \\
                  &+\gamma_{40}\text{age}_{k}\\
                  &+\gamma_{50}\text{gender}_k\\
                  &+\gamma_{60}\text{age}_k \times \text{gender}_k \\
                  &+\gamma_{11}\text{age}_{k}\times\text{condition}_{j} \\
                  &+\gamma_{21}\text{age}_{k}\times\text{information}_{j} \\
                  &+u_{0k} \\
                  &+u_{0j}
\end{align*}
$$
We can model the outcome $Y_{i(j,k)}$ using the Bernoulli distribution, where 
$\mu$ denotes the probability of success (teaching a complex fact to an adult or 
teaching a basic fact to a baby):
$$
\begin{align*}
Y_{i(j,k)}&\sim \text{Bernoulli}(\mu_{(j,k)})\\
\eta_{(j,k)}&=\text{logit}(\mu_{(j,k)})=\beta_{0(j,k)}\\
\mu_{(j,k)}&= \dfrac{\text{exp}(\eta_{(j,k)})}{1+\text{exp}(\eta_{(j,k)})}
\end{align*}
$$



### Effect size/coefficient estimate for the age variable

We can determine boundaries/values for some coefficients using  Wani and Henny's estimates for the odds of success in each age group.

Wani and Henny estimate that a 6 year old will be able to 
teach discriminatively (that a basic fact will be taught to a baby and a complex
fact will be taught to an adult) 2 out of 3 trials, giving us a probability
estimate of P(complex|adult)=P(basic|baby)=$\frac{2}{3}$ and 
P(basic|adult)=P(complex|baby)=$\frac{1}{3}$. Then, for 6 year olds,

$$
\begin{align*}
P(\text{complex}|\text{baby})=\dfrac{\text{exp}(\eta_{(j,k)})}{1+\text{exp}(\eta_{(j,k)})}&=\frac{1}{3}\\
2\times\text{exp}(\eta_{(j,k)})&=1\\
{\eta_{(j,k)}}_{|\text{baby}}&=-0.693\\
P(\text{complex}|\text{adult})=\dfrac{\text{exp}(\eta_{(j,k)})}{1+{\text{exp}(\eta_{(j,k)})}}&=\frac{2}{3}\\
\text{exp}(\eta_{(j,k)})&=2\\
{\eta_{(j,k)}}_{\text{|adult}}&=0.693\\
\end{align*}
$$

Substituting in the linear function and inserting 0 for
condition=baby and 1 for condition=adult,

$$
\begin{align*}
{\eta_{(j,k)}}_{\text{|baby}}&=\gamma_{00} \\
                  &+\gamma_{20}\text{information}_{j} \\
                  &+\gamma_{40}\text{age}_{k}\\
                  &+\gamma_{50}\text{gender}_k\\
                  &+\gamma_{60}\text{age}_k \times \text{gender}_k \\
                  &+\gamma_{21}\text{age}_{k}\times\text{information}_{j} \\
                  &+u_{0k} \\
                  &+u_{0j} \\
{\eta_{(j,k)}}_{\text{|adult}}&=\gamma_{00} \\
                  &+\gamma_{10} \\
                  &+\gamma_{20}\text{information}_{j} \\
                  &+\gamma_{40}\text{age}_{k}\\
                  &+\gamma_{50}\text{gender}_k\\
                  &+\gamma_{60}\text{age}_k \times \text{gender}_k \\
                  &+\gamma_{11}\text{age}_{k} \\
                  &+\gamma_{21}\text{age}_{k}\times\text{information}_{j} \\
                  &+u_{0k} \\
                  &+u_{0j}
\end{align*}
$$

Then we have
$$
\begin{align*}
{\eta_{(j,k)}}_{\text{adult}}-{\eta_{(j,k)}}_{\text{baby}}&=0.693+0.693\\
  1.386=&\gamma_{10}+\gamma_{11}\underbrace{\text{age}_{k}}_{1}\\
  1.386=&\gamma_{10}+\gamma_{11}
\end{align*}
$$

Wani and Henny predict that the 4 year olds will not be able to discriminatively
teach based on knowledge states, hence P(complex|adult)=P(basic|adult)=P(complex|baby)=P(basic|baby)= $\frac{1}{2}$.

Then, for 4 year olds,
$$
\begin{align*}
P(\text{complex}|\text{adult})=\mu_{(j,k)}&= \dfrac{\text{exp}(\eta_{(j,k)})}{1+\text{exp}(\eta_{(j,k)})}=\dfrac{1}{2}\\
\text{exp}(\eta_{(j,k)})&=1 \\
\eta_{(j,k)}&=0
\end{align*}
$$
Then we have
$$
\begin{align*}
{\eta_{(j,k)}}_{\text{|adult}}={\eta_{(j,k)}}_{\text{|baby}}&=0\\
{\eta_{(j,k)}}_{\text{adult}}-{\eta_{(j,k)}}_{\text{baby}}&=0\\
  0&=\gamma_{10}+\gamma_{11}\underbrace{\text{age}_{k}}_{0} \\
  0&=\gamma_{10}
\end{align*}
$$

Let's assume 8 year olds will be successful 3 out of 4 trials in either condition.
Then, 
$$
\begin{align*}
P(\text{complex}|\text{adult})=\dfrac{\text{exp}(\eta_{(j,k)})}{1+\text{exp}(\eta_{(j,k)})}&=\frac{3}{4}\\
\text{exp}(\eta_{(j,k)})&=3\\
{\eta_{(j,k)}}_{|\text{adult}}&=1.099\\
P(\text{complex}|\text{baby})=\dfrac{\text{exp}(\eta_{(j,k)})}{1+{\text{exp}(\eta_{(j,k)})}}&=\frac{1}{4}\\
3\times\text{exp}(\eta_{(j,k)})&=1\\
{\eta_{(j,k)}}_{\text{|baby}}&=-1.099\\
\end{align*}
$$
$$
\begin{align*}
{\eta_{(j,k)}}_{\text{adult}}-{\eta_{(j,k)}}_{\text{baby}}&=1.099+1.099\\
  2.198=&\gamma_{10}+\gamma_{11}\underbrace{\text{age}_{k}}_{1}\\
  2.198=&\gamma_{10}+\gamma_{11}
\end{align*}
$$
(assuming 8 year olds would be coded as 1 and 6 year olds would be coded as 0).

## Reduced model 2

Removing all effects but those associated with age and condition,

$$
\begin{align*}
\text{Y}_{i(j,k)}&=\gamma_{00} \\
                  &+\gamma_{10}\text{condition}_{j} \\
                  &+\gamma_{40}\text{age}_{k}\\
                  &+\gamma_{11}\text{age}_{k}\times\text{condition}_{j} \\
                  &+u_{0k} \\
                  &+u_{0j}
\end{align*}
$$
The above computations stand for this model.

For either reduced model, we assume 
$$
\begin{pmatrix}u_{0j}\\u_{0k}\end{pmatrix}
\sim N
\begin{pmatrix}
\begin{bmatrix}0\\0\end{bmatrix},
\begin{bmatrix}
\tau_{0j}^2 & \tau_{0k, 0j} \\
\tau_{0j,0k} & \tau_{0k}^2 \\
\end{bmatrix}
\end{pmatrix}.
$$


# Simulation prep

Steps:

1. Set parameter values for the age groups. 
2. Functions to simulate data following distributions defined by these parameters.
3. Use the functions above to simulate data. Repeat for large number of replications. 
4. Determine how many times the value was captured out of all replications.


```{r counterbalance-prep}
condord1 <- c("Baby", "Adult", "Adult", "Baby",
              "Adult", "Baby", "Baby", "Adult",
              "Baby", "Adult", "Adult", "Baby")
condord2 <- c("Adult", "Baby", "Baby", "Adult",
              "Baby", "Adult", "Adult", "Baby",
              "Adult", "Baby", "Baby", "Adult")

animord1 <- c("Pa", "Be", "Ti", "Bi", "Ze", "Fo",
              "Ra", "Ho", "De", "Tu", "Du", "Go")
animord2 <- c("Go", "Du", "Tu", "De", "Ho", "Ra",
              "Fo", "Ze", "Bi", "Ti", "Be", "Pa")
animord3 <- c("Be", "Ti", "Ze", "Pa", "Tu", "Go",
              "Du", "Ra", "Fo", "Bi", "Ho", "De")
animord4 <- c("De", "Ho", "Bi", "Fo", "Ra", "Du", 
              "Go", "Tu", "Pa", "Ze", "Ti", "Be")
inford1 <- c(rep("CB", 3), rep("BC", 3), rep("CB", 3), rep("BC", 3))
inford2 <- c(rep("BC", 3), rep("CB", 3), rep("BC", 3), rep("CB", 3))
inford3 <- c(rep("BC", 3), rep("CB", 3), rep("CB", 3), rep("BC", 3))
inford4 <- c(rep("CB", 3), rep("BC", 3), rep("BC", 3), rep("CB", 3))
```

```{r n-64-dataset-fixed}
n = 32
child <- as.factor(rep(c(1:n), each = 12)  )
condition <- c(rep(condord1, 16), rep(condord2, 16))
animal <- rep(c(animord1, animord2, animord3, animord4), 8)
information <- rep(c(inford1, inford2, inford3, inford4), 8)
gender <- rep(c(rep("F", 12), rep("M", 12), rep("M", 12), rep("F", 12), 
            rep("M", 12), rep("F", 12), rep("F", 12), rep("M", 12)), 4)

#expand to have 2 age groups, assuming we'll have the same counterbalancing
child2 <- as.factor(rep(c(1:(n*2)), each = 12)  )

condition2 <- c(condition, condition)
animal2 <- c(animal, animal)
information2 <- c(information, information)
gender2 <- c(gender, gender)
age <- c(rep("4", n*12), rep("6", n*12))

df64 <- as.data.frame(cbind("child" = child2, "animal"= animal2, 
                           "information" = information2, 
                           "condition" = condition2,
                           "gender" = gender2, 
                           "age" = age))
df64["age01"] <- ifelse(df64$age==4,0,1)
df64["gender01"] <- ifelse(df64$gender=="M",0,1)
df64["condition01"] <- ifelse(df64$condition=="Baby",0,1)
df64["information01"] <- ifelse(df64$information=="BC",0,1)

head(df64)
```

```{r n-80-dataset-fixed}
n = 40
child <- as.factor(rep(c(1:n), each = 12))
condition <- c(rep(condord1, 20), rep(condord2, 20))
animal <- rep(c(animord1, animord2, animord3, animord4), 10)
information <- rep(c(inford1, inford2, inford3, inford4), 10)
gender <- rep(c(rep("F", 12), rep("M", 12)), 20)

#expand to have 2 age groups
child2 <- as.factor(rep(c(1:(n*2)), each = 12))

condition2 <- c(condition, condition)
animal2 <- c(animal, animal)
information2 <- c(information, information)
gender2 <- c(gender, gender)
age <- c(rep("4", n*12), rep("6", n*12))

df80 <- as.data.frame(cbind("child" = child2, "animal"= animal2, 
                           "information" = information2, 
                           "condition" = condition2,
                           "gender" = gender2, 
                           "age" = age))
df80["age01"] <- ifelse(df80$age==4,0,1)
df80["gender01"] <- ifelse(df80$gender=="M",0,1)
df80["condition01"] <- ifelse(df80$condition=="Baby",0,1)
df80["information01"] <- ifelse(df80$information=="BC",0,1)
```

```{r n-96-dataset-fixed}
n = 48 # per age group
child <- as.factor(rep(c(1:n), each = 12)  )
condition <- c(rep(condord1, 24), rep(condord2, 24))
animal <- rep(c(animord1, animord2, animord3, animord4), 12)
information <- rep(c(inford1, inford2, inford3, inford4), 12)
gender <- rep(c(rep("F", 12), rep("M", 12)), 24)
child2 <- as.factor(rep(c(1:(n*2)), each = 12))

condition2 <- c(condition, condition)
animal2 <- c(animal, animal)
information2 <- c(information, information)
gender2 <- c(gender, gender)
age <- c(rep("4", n*12), rep("6", n*12))

df96 <- as.data.frame(cbind("child" = child2, "animal"= animal2, 
                           "information" = information2, 
                           "condition" = condition2,
                           "gender" = gender2, 
                           "age" = age))
df96["age01"] <- ifelse(df96$age==4, 0, 1)
df96["gender01"] <- ifelse(df96$gender=="M",0,1)
df96["condition01"] <- ifelse(df96$condition=="Baby",0,1)
df96["information01"] <- ifelse(df96$information=="BC",0,1)
```

## Functions

```{r gen-dataset-reduced1-func}
gen_dataset_red1 <- function(gamma00, gamma20, gamma40, gamma50, gamma60, 
                          gamma11, gamma21, gamma10_4, gamma10_6,
                          tau0jsq_4, tau0j0k_4, tau0ksq_4, 
                          tau0jsq_6, tau0j0k_6, tau0ksq_6,
                          df) {
  
info <- df$information01; cond <- df$condition01; age <- df$age01
gender <- df$gender01
   
# Generate the random components
covar_matrix_4 <- make.positive.definite(matrix(c(tau0jsq_4, tau0j0k_4,
                         tau0j0k_4, tau0ksq_4), ncol = 2), tol=1e-3)
random_comp_4 <- MASS::mvrnorm(n = 1, mu = c(0, 0), Sigma = covar_matrix_4)
u0j_4 <- random_comp_4[1]; u0k_4 <- random_comp_4[2]

covar_matrix_6 <- make.positive.definite(matrix(c(tau0jsq_6, tau0j0k_6, 
                         tau0j0k_6, tau0ksq_6), ncol = 2), tol=1e-3)
random_comp_6 <- MASS::mvrnorm(n = 1, mu = c(0, 0), Sigma = covar_matrix_6)
u0j_6 <- random_comp_6[1]; u0k_6 <- random_comp_6[2]

# Probabilities
eta_4_comp_adult <- gamma00 + gamma10_4 + gamma20*info + gamma40*age + 
  gamma50*gender + gamma60*age*gender + 
  gamma11*age + gamma21*age*info + u0j_4 + u0k_4

eta_4_comp_baby <- gamma00 + gamma20*info + gamma40*age +
  gamma50*gender + gamma60*age*gender + gamma21*age*info +
  u0j_4 + u0k_4

eta_6_comp_adult <- gamma00 + gamma10_6 + gamma20*info + 
  gamma40*age + gamma50*gender + gamma60*age*gender + 
  gamma11*age + gamma21*age*info + u0j_6 + u0k_6 

eta_6_comp_baby <- gamma00 + gamma20*info + gamma40*age +
  gamma50*gender + gamma60*age*gender + gamma21*age*info +
  u0j_6 + u0k_6 

p_4y_complex_adult <- exp(eta_4_comp_adult) / (1 + exp(eta_4_comp_adult))
p_4y_basic_baby <- 1 - exp(eta_4_comp_baby) / (1 + exp(eta_4_comp_baby))

p_6y_complex_adult <- exp(eta_6_comp_adult) / (1 + exp(eta_6_comp_adult))
p_6y_basic_baby <- 1 - exp(eta_6_comp_baby) / (1 + exp(eta_6_comp_baby))

df["y"] <- c(rep(NA, dim(df)[1]))

for (i in seq_along(1:dim(df)[1])) {
  if (df[i, "age"]=="4"){
    if (df[i, "condition"]=="adult") {
      df[i, "y"] <- as.numeric(rbinom(1, 1, p_4y_complex_adult))
      } else {
      df[i, "y"] <- as.numeric(rbinom(1, 1, p_4y_basic_baby))
      }
  }
  if (df[i, "age"]=="6"){
    if (df[i, "condition"]=="adult") {
      df[i, "y"] <- as.numeric(rbinom(1, 1, p_6y_complex_adult))
      } else {
      df[i, "y"] <- as.numeric(rbinom(1, 1, p_6y_basic_baby))
      }
  }
}
return(df)
}
```


```{r gen-dataset-reduced2-func}
gen_dataset_red2 <- function(gamma00, gamma40,  gamma11, gamma10_4, gamma10_6, 
                             tau0jsq_4, tau0j0k_4, tau0ksq_4, 
                             tau0jsq_6, tau0j0k_6, tau0ksq_6,
                             df) {
info <- df$information01; cond <- df$condition01; age <- df$age01
gender <- df$gender01

# Generate the random components
covar_matrix_4 <- make.positive.definite(matrix(c(tau0jsq_4, tau0j0k_4,
                         tau0j0k_4, tau0ksq_4), ncol = 2), tol=1e-3)
random_comp_4 <- MASS::mvrnorm(n = 1, mu = c(0, 0), Sigma = covar_matrix_4)
u0j_4 <- random_comp_4[1]; u0k_4 <- random_comp_4[2]

covar_matrix_6 <- make.positive.definite(matrix(c(tau0jsq_6, tau0j0k_6, 
                         tau0j0k_6, tau0ksq_6), ncol = 2), tol=1e-3)
random_comp_6 <- MASS::mvrnorm(n = 1, mu = c(0, 0), Sigma = covar_matrix_6)
u0j_6 <- random_comp_6[1]; u0k_6 <- random_comp_6[2]

# Probabilities

eta_4_comp_adult <- gamma00 + gamma10_4 + gamma40*age + gamma11*age + u0j_4 + u0k_4 
eta_4_comp_baby <- gamma00 + gamma40*age + u0j_4 + u0k_4 

eta_6_comp_adult <- gamma00 + gamma10_6 + gamma40*age + gamma11*age  + u0j_6 + u0k_6
eta_6_comp_baby <- gamma00 +  gamma40*age + u0j_6 + u0k_6 

p_4y_complex_adult <- exp(eta_4_comp_adult) / (1 + exp(eta_4_comp_adult))
p_4y_basic_baby <- 1 - exp(eta_4_comp_baby) / (1 + exp(eta_4_comp_baby))

p_6y_complex_adult <- exp(eta_6_comp_adult) / (1 + exp(eta_6_comp_adult))
p_6y_basic_baby <- 1 - exp(eta_6_comp_baby) / (1 + exp(eta_6_comp_baby))

df["y"] <- c(rep(NA, dim(df)[1]))

for (i in seq_along(1:dim(df)[1])) {
  if (df[i, "age"]=="4"){
    if (df[i, "condition"]=="adult") {
      df[i, "y"] <- as.numeric(rbinom(1, 1, p_4y_complex_adult))
      } else {
      df[i, "y"] <- as.numeric(rbinom(1, 1, p_4y_basic_baby))
      }
  }
  if (df[i, "age"]=="6"){
    if (df[i, "condition"]=="adult") {
      df[i, "y"] <- as.numeric(rbinom(1, 1, p_6y_complex_adult))
      } else {
      df[i, "y"] <- as.numeric(rbinom(1, 1, p_6y_basic_baby))
      }
  }
}
return(df)
}
```



## Setting parameters

Based on the calculations above and discussions with Wani, 

- $\gamma_{00}=0$: predicted log-odds when condition, information, age, gender, 
and $\mu_{0k}$ and $\mu_{0j}$ are 0. In other words, predicted log odds of a 4
year old male child's successful discriminative teaching when the audience is a
baby, the basic fact is presented first, and the random slopes are 0. Since 
Wani and Henny predict that 4 year olds would be able to teach differentially with
a probability of 0.5, set $\gamma_{00}=0$.

- $\gamma_{20}=0.001$: predicted difference in log-odds associated with the complex
fact being presented first as opposed to the basic fact.

- $\gamma_{40}=1.5$: predicted difference in log-odds associated with the 
participant being a 6 year old as opposed to a 4 year old. 

- $\gamma_{50}=0.001$: predicted difference in log-odds associated with the 
participant being a female as opposed to a male. 

- $\gamma_{60}=0.01$: predicted deviation of the slope of age in log-odds associated 
with the participant being a female as opposed to a male. 

- $\gamma_{21=0.001}$: predicted deviation of the slope of age in log-odds associated 
with the complex fact being presented first as opposed to the basic fact presented
first.

- $u_{0k}$: child k's deviation in log-odds and $u_{0j}$: animal j's deviation in log-odds. Variance matrix values for 4 year olds: $\tau_{0j}^2=0.2$, $\tau_{0j, 0k}=0$, $\tau_{0k}^2=0.8$. Variance matrix values for 6 year olds: $\tau_{0j}^2=0.2$, $\tau_{0j, 0k}=0$, $\tau_{0k}^2=1$.

Earlier, we computed $\gamma_{10|4y}=0$, $\gamma_{10|6y}+\gamma_{11}=1.386$, and 
$\gamma_{10|8y}+\gamma_{11}=2.198$.
$\gamma_{10|6y}=\gamma_{11}=0.693$ or $\gamma_{10|6y}=0.462$ and $\gamma_{10|6y}=\gamma_{11}=0.924$ are some possible values for 6 year olds. 
Similarly, $\gamma_{10|8y}=\gamma_{11}=1.099$. We only need to set $\gamma_{11}$ 
since age=0 will cancel terms for one group.

- $\gamma_{11}$: predicted deviation of the slope of age in log-odds associated 
with the audience being an adult as opposed to a baby.
- $\gamma_{10}$: predicted difference in log-odds associated with the audience 
being an adult as opposed to a baby (so switching from 0 to 1).

```{r set-parameters}
gamma00 <- 0
gamma20 <- 0.001 
gamma40 <- 1.5
gamma50 <-  0.001
gamma60 <- 0.01
gamma21 <- 0.001
gamma10_4 <- 0
gamma10_6 <- 0.693
gamma11 <- 0.693
  
# random comp
tau0jsq_4 <- 0.2
tau0j0k_4 <- 0
tau0ksq_4 <- 0.8
tau0jsq_6 <- 0.2
tau0j0k_6 <-0
tau0ksq_6 <- 1

niter = 1000
```


# Simulate data, compute power 

```{r red1-df64, message=FALSE, warning=FALSE}
set.seed(77)
datsets_1_64 <- models_1_64 <-  sig_1_64 <- vector(mode="list", niter)
try(
for (i in 1:(niter)){
  datsets_1_64[[i]] <- gen_dataset_red1(gamma00, gamma20, gamma40, 
                                   gamma50, gamma60, gamma11, 
                                   gamma21, gamma10_4, gamma10_6, 
                                   tau0jsq_4, tau0j0k_4, tau0ksq_4, 
                                   tau0jsq_6, tau0j0k_6, tau0ksq_6, df=df64)
  models_1_64[[i]] <- summary(glmmTMB(y ~ condition01 + information01 + age01 +
                                   gender01 + age01*gender01 + age01*condition01 +
                                   age01*information01 + (1 | animal) + (1 | child),
                                   data = datsets_1_64[[i]],
                                   family = binomial("logit"),
                                   REML = TRUE))
  sig_1_64[i] <- models_1_64[[i]]$coefficients[[1]][28]
}
)
sum(as.numeric(unlist(sig_1_64)<0.05))/1000

#674/1000
```

```{r red1-df64-gamma11-10diff, message=FALSE, warning=FALSE}
set.seed(77)
gamma11 <- 0.924
gamma10_6 <- 0.462

datsets_1_64_g <- models_1_64_g <-  sig_1_64_g <- vector(mode="list", niter)
try(
for (i in 1:(niter)){
  datsets_1_64_g[[i]] <- gen_dataset_red1(gamma00, gamma20, gamma40, 
                                      gamma50, gamma60, gamma11, 
                                      gamma21, gamma10_4, gamma10_6, 
                                      tau0jsq_4, tau0j0k_4, tau0ksq_4, 
                                      tau0jsq_6, tau0j0k_6, tau0ksq_6, df=df64)
  models_1_64_g[[i]] <- summary(glmmTMB(y ~ condition01 + information01 + age01 +
                                   gender01 + age01*gender01 + age01*condition01 +
                                   age01*information01 + (1 | animal) + (1 | child),
                                   data = datsets_1_64_g[[i]],
                                   family = binomial("logit"),
                                   REML = TRUE))
  sig_1_64_g[i] <- models_1_64_g[[i]]$coefficients[[1]][28]
}
)
sum(as.numeric(unlist(sig_1_64_g)<0.05))/1000

#0.674/1000

gamma10_6 <- 0.693
gamma11 <- 0.693
```

```{r red1-df64-no-age-info-int, message=FALSE, warning=FALSE}
# removing the interaction term of age and information order
datsets_1_64_inf <- models_1_64_inf <- sig_1_64_inf <- vector(mode="list", niter)
try(
for (i in 1:(niter)){
  datsets_1_64_inf[[i]] <- gen_dataset_red1(gamma00, gamma20, gamma40, 
                                   gamma50, gamma60, gamma11, 
                                   gamma21, gamma10_4, gamma10_6, 
                                   tau0jsq_4, tau0j0k_4, tau0ksq_4, 
                                   tau0jsq_6, tau0j0k_6, tau0ksq_6, df=df64)
  models_1_64_inf[[i]] <- summary(glmmTMB(y ~ condition01 + information01 + age01 +
                                   gender01 + age01*gender01 + age01*condition01 +
                                   (1 | animal) + (1 | child),
                                   data = datsets_1_64_inf[[i]],
                                   family = binomial("logit"),
                                   REML = TRUE))
  sig_1_64_inf[i] <- models_1_64_inf[[i]]$coefficients[[1]][25]
}
)
sum(as.numeric(unlist(sig_1_64_inf)<0.05))/1000

#728/1000
```


```{r red2-df64,message=FALSE, warning=FALSE}
datsets_2_64 <- models_2_64 <- sig_2_64 <- vector(mode="list", niter)
try(
for (i in 1:(niter)){
    datsets_2_64[[i]] <- gen_dataset_red2(gamma00, gamma40,  gamma11, 
                                      gamma10_4, gamma10_6, 
                                      tau0jsq_4, tau0j0k_4, tau0ksq_4, 
                                      tau0jsq_6, tau0j0k_6, tau0ksq_6,df=df64)
  models_2_64[[i]] <- summary(glmmTMB(y ~ condition01 + age01 + age01*condition01 +
                                    (1 | animal) + (1 | child),
                                    data = datsets_2_64[[i]],
                                    family = binomial("logit"),
                                    REML = TRUE))
  sig_2_64[i] <- models_2_64[[i]]$coefficients[[1]][15]
}
)
sum(as.numeric(unlist(sig_2_64)<0.05))/1000
#778/1000
```




```{r red1-df80, message=FALSE, warning=FALSE}
datsets_1_80 <- models_1_80 <- sig_1_80 <- vector(mode="list", niter)
try(
for (i in 1:(niter)){
  datsets_1_80[[i]] <- gen_dataset_red1(gamma00, gamma20, gamma40, gamma50, gamma60, 
                          gamma11, gamma21, gamma10_4, gamma10_6,
                          tau0jsq_4, tau0j0k_4, tau0ksq_4, 
                          tau0jsq_6, tau0j0k_6, tau0ksq_6, df=df80)
  models_1_80[[i]] <- summary(glmmTMB(y ~ condition01 + information01 + age01 +
                                   gender01 + age01*gender01 + age01*condition01 +
                                   age01*information01 + (1 | animal) + (1 | child),
                                   data = datsets_1_80[[i]],
                                   family = binomial("logit"),
                                   REML = TRUE))
  sig_1_80[i] <- models_1_80[[i]]$coefficients[[1]][28]
}
)
sum(as.numeric(unlist(sig_1_80)<0.05))/1000
#723/1000
```


```{r red2-df80, message=FALSE, warning=FALSE}
datsets_2_80 <- models_2_80 <- sig_2_80 <- vector(mode="list", niter)
try(
for (i in 1:(niter)){
  datsets_2_80[[i]] <- gen_dataset_red2(gamma00, gamma40,  gamma11, 
                                      gamma10_4, gamma10_6, 
                                      tau0jsq_4, tau0j0k_4, tau0ksq_4, 
                                      tau0jsq_6, tau0j0k_6, tau0ksq_6, df=df80)
  models_2_80[[i]] <- summary(glmmTMB(y ~ condition01 + age01 + age01*condition01 +
                                    (1 | animal) + (1 | child),
                                    data = datsets_2_80[[i]],
                                    family = binomial("logit"),
                                    REML = TRUE))
  sig_2_80[i] <- models_2_80[[i]]$coefficients[[1]][15]
}
)
sum(as.numeric(unlist(sig_2_80)<0.05))/1000
#813/1000
```




```{r red1-df96, message=FALSE, warning=FALSE}
set.seed(777)
datsets_1_96 <- models_1_96 <-  sig_1_96 <- vector(mode="list", niter)
try(
for (i in 1:(niter)){
  datsets_1_96[[i]] <- gen_dataset_red1(gamma00, gamma20, gamma40, gamma50, gamma60, 
                          gamma11, gamma21, gamma10_4, gamma10_6,
                          tau0jsq_4, tau0j0k_4, tau0ksq_4, 
                          tau0jsq_6, tau0j0k_6, tau0ksq_6, df=df96)
  models_1_96[[i]] <- summary(glmmTMB(y ~ condition01 + information01 + age01 +
                                   gender01 + age01*gender01 + age01*condition01 +
                                   age01*information01 + (1 | animal) + (1 | child),
                                   data = datsets_1_96[[i]],
                                   family = binomial("logit"),
                                   REML = TRUE))
  sig_1_96[i] <- models_1_96[[i]]$coefficients[[1]][28]
}
)
sum(as.numeric(unlist(sig_1_96)<0.05))/1000

#727/1000
```


```{r red2-df96,message=FALSE, warning=FALSE}
datsets_2_96 <- models_2_96 <- sig_2_96 <- vector(mode="list", niter)
try(
for (i in 1:(niter)){
  datsets_2_96[[i]] <- gen_dataset_red2(gamma00, gamma40,  gamma11, 
                                      gamma10_4, gamma10_6, 
                                      tau0jsq_4, tau0j0k_4, tau0ksq_4, 
                                      tau0jsq_6, tau0j0k_6, tau0ksq_6, df=df96)
  models_2_96[[i]] <- summary(glmmTMB(y ~ condition01 + age01 + age01*condition01 +
                                    (1 | animal) + (1 | child),
                                    data = datsets_2_96[[i]],
                                    family = binomial("logit"),
                                    REML = TRUE))
  sig_2_96[i] <- models_2_96[[i]]$coefficients[[1]][15]
}
)
sum(as.numeric(unlist(sig_2_96)<0.05))/1000
#813/1000
```